An event-sourced and decentralized database with IPLD and materialized views

### 2019-09-27 draft.tex
draft: add blurb about redux front-end connection
Signed-off-by: Carson Farmer <carson.farmer@gmail.com>

>>>>

\subsubsection{Tighter Coupling with Front End Models}\label{sec:coupling}

Implementing Threads internals (see Section \ref{sec:internals}) using similar patterns to common frontend workflows (e.g., Redux) presents opportunities for tighter coupling between ``backend'' logic and fontend views. This is a major advantage of tools such as reSolve\footnote{\url{https://reimagined.github.io/resolve/}}, where ``system changes can be reflected immediately [on the frontend], without the need to re-query the backend'' \cite{ereminReduxInspiredBackend2019}. Textile developers will develop frameworks to more directly expose the internals of Threads to frontend SDKs, making it possible to sync application state across and between apps and services on the Textile network.
